The Stakes of Scrying: \\ \lstinline[style=inlinecode]{.^} dotket and the Seer Proposal

### 2024-04-10 mss.tex
Proof

\newcommand{\authorname}{Ted Blackman~\patp{rovnys-ricfer} \\ Paul Driver~\patp{fodwyt-ragful}}
\newcommand{\authorpatp}{}
\newcommand{\affiliation}{Urbit Foundation}

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:1 (2024):  35–46. \\
              ~ \\
              Address author correspondence to \patp{rovnys-ricfer}.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{\lstinline[style=inlinecode]{.^} dotket and the Seer Proposal}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{35}

@@

\sloppy
The Arvo kernel's scry handler gate, as described in the original Moron Lab blog post about Urbit \citep{Yarvin2010}, is a ``static functional namespace''; even though that gate changes frequently, it maintains the invariant that every scry path's binding to a value is immutable.\footnote{Up to some known concerns that are addressed by UIP-0116: Arvo Ticks \citetpr{UIP-0116}.}

@@

The current reference implementation of Seer is available at \citetpr{Levan2023}.  A more complete example is available at \citealt{Levan2023a}.

@@

Because of these concerns with the proposed move-based replacement for \dotket, we will first add it as a new feature alongside \dotket~before committing to removing \dotket.  In this way, if the application patterns end up suffering inordinately, \dotket~may be retained.  That being said, the current primary plan is to deprecate \dotket~once move-based scrying has been verified as providing a sufficiently good application model.  This is a conservative, incremental approach that will not break any existing code and lets us try out the new style in production applications before committing to the removal of Nock 12.

>>>>

\newcommand{\authorname}{Ted Blackman~\patp{rovnys-ricfer} \\ Paul Driver~\patp{fodwyt-ragful} \\ Matthew Levan~\patp{mastyr-bottec}}
\newcommand{\authorpatp}{}
\newcommand{\affiliation}{Urbit Foundation}

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:1 (2024):  47–58. \\
              ~ \\
              Address author correspondence to \patp{rovnys-ricfer}.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{\lstinline[style=inlinecode]{.^} dotket and the Seer Proposal}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{47}

@@

\sloppy
The Arvo kernel's scry handler gate, as described in the original Moron Lab blog post about Urbit \citep{Yarvin2010}, is a ``static functional namespace''; even though that gate changes frequently, it maintains the invariant that every scry path's binding to a value is immutable.\footnote{Up to some known concerns that are addressed by Arvo Ticks \citetpr{UIP-0116}.}

@@

The current reference implementation of Seer is available at \texttt{urbit/urbit} \citetpr{Levan2023}.  A more complete example is available at \citealt{Levan2023a}.

@@

Because of these concerns with the proposed move-based replacement for \dotket, we will first add it as a new feature alongside \dotket~before committing to removing \dotket.  In this way, if the application patterns end up suffering inordinately, \dotket~may be retained.  That being said, the current primary plan is to deprecate \dotket~once move-based scrying has been verified as providing a sufficiently good application model.  This is a conservative, incremental approach that will not break any existing code and lets us try out the new style in production applications before committing to the removal of Nock 12.  \tombstone{}
